MINOS Handover Plots

### 2023-07-15 minos/validation/cross_validation_default.Rmd
Added active var to handovers and cross-validation
tuning for final paper2 handovers and crossval

#cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

>>>>

#cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
# getting only people who were in 2014 population. 
who_2014_pidps <- raw.dat %>% filter(time %in% c(2014) & hh_income<10000) %>% select(pidp) %>% unique()
raw <- raw.dat %>% filter(time %in% cv.years)
raw <- raw %>% filter (pidp %in% who_2014_pidps$pidp)

### 2023-07-15 minos/validation/handovers.Rmd
tuning for final paper2 handovers and crossval

```{r}
handover_continuous(raw.dat, base.dat, var = 'hh_income')
```

@@

## SF_12_MCS

```{r}
handover_continuous(raw.dat, base.dat, var = 'SF_12_MCS')
```

@@

```{r}
raw.sf12.m <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12.m <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)

spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

rm(raw.sf12.m, base.sf12.m, sf12.m.spag)
```

## SF_12_PCS

```{r}
handover_continuous(raw.dat, base.dat, var = 'SF_12_PCS')
```

```{r}
raw.sf12.p <- raw.dat %>%
  select(pidp, age, time, SF_12_PCS)
base.sf12.p <- base.dat %>%
  select(pidp, age, time, SF_12_PCS)

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)

spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
```

## Financial Situation

```{r}
handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
```

## Housing Quality

```{r}
handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'housing_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

## Neighbourhood Safety

```{r}
handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

## Loneliness

```{r}
handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
handover_continuous(raw.dat, base.dat, var = 'nutrition_quality')
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.s <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
handover_continuous(raw.dat, base.dat, var = 'phealth')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, phealth)
base.s <- base.dat %>%
  select(pidp, age, time, phealth)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'phealth',
             save = shall.we.save,
             save.path = save.path)

rm(raw.s, base.s, spag)
```

## Education

```{r}
handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

## Alcohol (AUDITC)

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
```

## Physical Activity

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
```

>>>>

```{r}
# first figure out how to plot final_US
# start with hh_income

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")

# raw.income2 <- raw.dat %>% 
#               dplyr::select(pidp, time, hh_income) %>%
#               filter(pidp %in% raw.income.wave1)
# 
# base.income <-  base.income2 <- base.dat %>%
#                                 dplyr::select(pidp, time, hh_income) %>%
#                                 filter(pidp %in% raw.income.wave1)
# 
# handover_lineplots(raw.d)
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.income2 <- raw.dat %>% 
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1) %>%
#   group_by(time) %>%
#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.income2 <- base.dat %>%
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1) %>%
#   group_by(time) %>%
#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# income2 <- rbind(raw.income2, base.income2)
# 
# # Now plot
# ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Household Income') +
#   xlab('Year') +
#   ylab('Income')
# 
# if (shall.we.save) {
#   ggsave(filename = 'hh_income_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# raw.income.check <- raw.dat %>% 
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1)
# 
# base.income.check <- base.dat %>%
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1)
# 
# rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#    raw.income.check, base.income.check)
```

@@

## SF12

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")
# 
# raw.sf12 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# # merge before plot
# sf12 <- rbind(raw.sf12, base.sf12)
# 
# # Now plot
# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_smooth() +
#   #geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
#   xlab('Year') +
#   ylab('SF12')
# 
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.sf12.2 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12.2 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
# 
# # Now plot
# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
#   xlab('Year') +
#   ylab('SF12')
# 
# if (shall.we.save) {
#   ggsave(filename = 'SF12_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

spaghetti_plot(sf12.spag, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

<!-- ## Financial Situation -->

<!-- ```{r} -->
<!-- raw.financial_situation <- raw.dat %>%  -->
<!--   dplyr::select(pidp, time, financial_situation) %>% -->
<!--   group_by(time, financial_situation) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.financial_situation <- base.dat %>% -->
<!--   dplyr::select(pidp, time, financial_situation) %>% -->
<!--   group_by(time, financial_situation) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- financial_situation <- rbind(raw.financial_situation, base.financial_situation) -->
<!-- financial_situation$financial_situation <- as.factor(financial_situation$financial_situation) -->

<!-- # Now plot -->
<!-- ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Financial Situation', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- financial_situation.norm <- financial_situation %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Financial situation') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'financial_situation.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.financial_situation, base.financial_situation, financial_situation, financial_situation.norm) -->
<!-- ``` -->

<!-- ## Housing Quality -->

<!-- ```{r} -->
<!-- raw.housing <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.housing <- base.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- housing <- rbind(raw.housing, base.housing) -->
<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->

<!-- # Now plot -->
<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- housing.norm <- housing %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'housing_quality.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- raw.s <- raw.dat %>% -->
<!--   select(pidp, age, time, housing_quality) -->
<!-- base.s <- base.dat %>% -->
<!--   select(pidp, age, time, housing_quality) -->

<!-- spag <- rbind(raw.s, base.s) -->

<!-- spaghetti_plot(spag, 'housing_quality', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->

<!-- rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Neighbourhood Safety -->

<!-- ```{r} -->
<!-- raw.neighbour <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.neighbour <- base.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->

<!-- # Now plot -->
<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- neighbour.norm <- neighbour %>% -->
<!--   group_by(time) %>% -->
<!--   filter(neighbourhood_safety != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'neighbourhood_safety.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- raw.s <- raw.dat %>% -->
<!--   select(pidp, age, time, neighbourhood_safety) -->
<!-- base.s <- base.dat %>% -->
<!--   select(pidp, age, time, neighbourhood_safety) -->

<!-- spag <- rbind(raw.s, base.s) -->

<!-- spaghetti_plot(spag, 'neighbourhood_safety', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->

<!-- rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Loneliness -->

<!-- ```{r} -->
<!-- raw.loneliness <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.loneliness <- base.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->

<!-- # Now plot -->
<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- loneliness.norm <- loneliness %>% -->
<!--   group_by(time) %>% -->
<!--   filter(loneliness != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'loneliness.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- raw.s <- raw.dat %>% -->
<!--   select(pidp, age, time, loneliness) -->
<!-- base.s <- base.dat %>% -->
<!--   select(pidp, age, time, loneliness) -->

<!-- spag <- rbind(raw.s, base.s) -->

<!-- spaghetti_plot(spag, 'loneliness', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->

<!-- rm(raw.s, base.s, spag) -->
<!-- ``` -->

@@

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
handover_lineplots(raw.dat, base.dat, 'nutrition_quality')

# Try a version where final_US is limited to only those present from wave 1
# onwards because the sample refreshments are messing with the plot
# raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.nut2 <- raw.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   filter(nutrition_quality >= 0) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.nut2 <- base.dat %>%
#   dplyr::select(pidp, time, nutrition_quality) %>%
#   filter(pidp %in% raw.wave1) %>%
#   group_by(time) %>%
#   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# nutrition_quality2 <- rbind(raw.nut2, base.nut2)
# 
# # Now plot
# ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Nutrition Quality') +
#   xlab('Year') +
#   ylab('Nutrition Quality')
# 
# if (shall.we.save) {
#   ggsave(filename = 'nutrition_quality_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2,
#     nutrition_quality2)
```

@@

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.nut <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "nutrition_quality", 
               save = T, 
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

<!-- ## Physical Health -->

<!-- NOTE: At present, physical health is not predicted or transitioned. -->

<!-- ```{r} -->
<!-- # first figure out how to plot final_US -->
<!-- # start with hh_income -->
<!-- raw.phealth <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- phealth <- rbind(raw.phealth, base.phealth) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
<!-- # onwards because the sample refreshments are messing with the plot -->
<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->

<!-- raw.phealth2 <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth2 <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'physical_health_wav1.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->
<!-- } -->

<!-- #raw.phealth.check <- raw.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- #base.phealth.check <- base.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
<!-- #rm(raw.phealth.check, base.phealth.check) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- raw.s <- raw.dat %>% -->
<!--   select(pidp, age, time, phealth) -->
<!-- base.s <- base.dat %>% -->
<!--   select(pidp, age, time, phealth) -->

<!-- spag <- rbind(raw.s, base.s) -->

<!-- spaghetti_plot(spag, 'phealth', -->
<!--              save = shall.we.save, -->
<!--              save.path = save.path) -->

<!-- rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ## Education -->

<!-- ```{r} -->
<!-- prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state') -->

<!-- var <- prepped.list$var -->
<!-- norm <- prepped.list$norm -->

<!-- tit <- 'Education State' -->

<!-- # Now plot -->
<!-- ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = tit, subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = tit) + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- if (shall.we.save) { -->
<!--   ggsave(filename = 'education_state.png', -->
<!--          plot = last_plot(), -->
<!--          path = save.path) -->
<!-- } -->

<!-- rm(prepped.list, var, norm, tit) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- pivoted <- combine_and_pivot_long(df1 = base.dat,  -->
<!--                                        df1.name = 'simulated',  -->
<!--                                        df2 = raw.dat,  -->
<!--                                        df2.name = 'raw',  -->
<!--                                        var = 'education_state') -->

<!-- cv_ordinal_plots(pivoted.df = pivoted,  -->
<!--                  var = 'education_state', -->
<!--                  save = shall.we.save, -->
<!--                  save.path = save.path) -->
<!-- ``` -->

<!-- ### Spaghetti -->

<!-- ```{r} -->
<!-- raw.s <- raw.dat %>% -->
<!--   select(pidp, age, time, education_state) -->
<!-- base.s <- base.dat %>% -->
<!--   select(pidp, age, time, education_state) -->

<!-- spag <- rbind(raw.s, base.s) -->

<!-- spaghetti_plot(spag, 'education_state', -->
<!--                save = shall.we.save, -->
<!--                save.path = save.path) -->

<!-- rm(raw.s, base.s, spag) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- ``` -->
